Untitled CAV Paper

### 2016-01-10 paper.tex
Definitions of games/synthesis

Reactive synthesis is formalised as a game between the \emph{system} and its
\emph{environment}. In this work we focus on safety games, in which the system
must prevent the environment from forcing the game into an error state. Much of
the complexity of reactive synthesis stems from tracking the set of states in
which a player is winning.

@@

Advances in SAT solving technology has prompted research into its applicability
to synthesis as an alternative to BDDs. One approach is to find sets of states
in CNF \cite{demiurge}. Another approach is to eschew states and focus on
\emph{runs} of the game. Previous work has applied this idea to solving
bounded games \cite{nina} by forming abstract trees of individual runs. In this
paper, we extend this idea to unbounded games by constructing approximate sets
of winning states from abstract trees.

@@

>>>>

Reactive synthesis is formalised as a game between the \emph{controller} and
its \emph{environment}. In this work we focus on safety games, in which the
controller must prevent the environment from forcing the game into an error
state.  Much of the complexity of reactive synthesis stems from tracking the
set of states in which a player is winning.

@@

Advances in SAT solving technology has prompted research into its applicability
to synthesis as an alternative to BDDs. One approach is to find sets of states
in CNF \cite{demiurge}. Another approach is to eschew states and focus on
\emph{runs} of the game. Previous work has applied this idea to realizability
of bounded games \cite{nina} by forming abstract representations of the game.
In this paper, we extend this idea to unbounded games by constructing
approximate sets of winning states from abstract trees.

@@

A \emph{safety game}, $G = \langle X, L_c, L_u, \delta, I, E, \rangle$,
consists of a set of state variables, sets of controllable and uncontrollable
label variables, a transition relationship $\delta : (X, L_c, L_u) \to X$, an
initial state, and an error state. The \emph{controller} and \emph{environment}
players choose controllable and uncontrollable labels respectively and the game
proceeds according to $\delta$.

An \emph{run} of a game $(x_0, c_0, u_0), (x_1, c_1, u_1) \dots (x_n, c_n,
u_n)$ is a chain of state and label pairs of length $n$ s.t.  $x_{k+1}
\leftarrow \delta(x_k, c_k, u_k)$. A run is winning for the controller if $x_0
= I \land \forall i \in \{1..n\} (x_i \neq E)$. In a bounded game of rank $n$
all runs are restricted to length $n$, whereas unbounded games consider runs of
infinite length.

A \emph{controller strategy} $\pi^c : X \to L_c$ is a mapping of states to
controllable labels. A controller strategy is winning in a bounded game of rank
$n$ if all runs $(x_0, \pi^c(x_0), u_0), (x_1, \pi^c(x_1), u_1) \dots (x_n,
\pi^c(x_n), u_n)$ are winning. Bounded \emph{realizability} is the problem of
determining the existence of such a strategy for a bounded game.

An \emph{environment strategy} $\pi^e : (X, L_c) \to L_u$ is a mapping of
states and controllable labels to uncontrollable labels. A bounded run is
winning for the environment if $x_0 = I \land \exists i \in \{1..n\} (x_i = E)$
and an environment strategy is winning for a bounded game if there exists a run
$(x_0, c_1, \pi^e(x_1, c_1)), (x_1, c_1, \pi^e(x_1, c_1)) \dots (x_n, c_n,
\pi^e(x_n, c_n))$ that wins for the environment. Safety games are zero sum,
therefore the existence of a controller strategy implies the nonexistence of an
environment strategy and vice versa.

A set of runs for a bounded game of rank $n$ can be represented by a \emph{game
tree} of depth $n$ with states in the nodes and labels as edges. A
\emph{strategy tree} similarly represents a strategy by restricting the edges
in a game tree to obey $\pi^c$ for a controller strategy or $\pi^e$ for an
environment strategy.

\subsection{Abstract Game Trees}

The bounded synthesis algorithm from \cite{nina} constructs abstractions of the
game in the form of \emph{abstract game trees}.
